Forecasting the 2024 U.S. Presidential Election Using a Model-Based Approach

### 2024-11-02 paper/paper.qmd
update estimand
Add more result

---
title: "Forecasting the 2024 U.S. Presidential Election Using a Model-Based Approach"
subtitle: "Harris expects to win on 49%, leads Trump by about 2% in 2024 US election"
author: 
  - Diana Shen
  - Jinyan Wei
  - Jerry Yu
thanks: "Code and data are available at: [https://github.com/DianaShen1224/Forecast-2024-US-election](https://github.com/DianaShen1224/Forecast-2024-US-election)."
date: today
date-format: long
abstract: "This paper predicts the outcome of the 2024 U.S. presidential election using a statistical model based on aggregated polling data for Kamala Harris and Donald Trump. We employ multi-level regression with post-stratification (MRP) using demographic predictors to estimate voter support. The analysis addresses polling biases and proposes an idealized survey methodology with a $100,000 budget. Our results offer insights into voter behavior and suggest improvements for future election forecasting models."
format: pdf
number-sections: true
bibliography: references.bib
editor: 
  markdown: 
    wrap: 72
---

@@

# Introduction

@@

# Data {#third-data}

## Overview

@@

## Measurement

@@

## Outcome variable

### The support percentage of Kamala Harris.

@@

## Predictor variables

### End Date

@@

### State

@@

### Pollster

@@

### Numeric Grade

@@

## Relationships between key varaibles

@@

## Model {#forth-model}

@@

### 3.1 Model Set-Up

@@

-   **National Poll (`national_poll`)**: Represents the national trend
    in support for the candidate.
-   **Pollster (`pollster`)**: Categorical variable identifying the
    organization conducting the poll, accounting for differences in
    methodology and reliability.
-   **Population (`population`)**: Reflects demographic or regional
    characteristics associated with each poll.

#### Unweighted Model

@@

$$
y_i | \mu_i, \sigma \sim \text{Normal}(\mu_i, \sigma)
$$ $$
\mu_i = \beta_0 + \beta_1 \cdot \text{National Poll}_i + \beta_2 \cdot \text{Pollster}_i + \beta_3 \cdot \text{Population}_i + \epsilon_i
$$ $$
\epsilon_i \sim \text{Normal}(0, \sigma^2)$$ Where:

-   $\beta_0$ is the intercept term, representing the baseline level of
    support.
-   $\beta_1, \beta_2, \beta_3$ are the coefficients for each predictor,
    indicating their influence on Harris's support percentage.
-   $\sigma^2$ is the variance of the error term, representing
    unobserved variability in support.

@@

### 3.1.1 Weighted Model Explanation

@@

- **Combined Weight**: The final weight is the product of all individual weights: $$
\text{Combined Weight} =\text{Recency Weight} \times \text{Sample Size Weight}
$$. This comprehensive weight prioritizes recent, large-sample, high-quality, and moderately frequent polls, creating a balanced and reliable dataset that reflects both current sentiment and credible data sources.

The **combined weight** for each poll is thus:

@@

### 3.1.2 Model Justification

@@

# Result

## Predicted Voting Outcomes

@@

## Recent Three Months Support Trends Linear Model Prediction

```{r}
#| echo: false
#| warning: false
#| message: false
#| include: false
####### Prediction and Plot ######
set.seed(233)
####### Prediction for Harris ######
new_data_harris <- data.frame(
  end_date = seq(
    min(harris_data$end_date),
    max(harris_data$end_date),
    length.out = 2000
  ),
  state = factor(sample( c("National","Arizona", "Georgia", "Michigan", "Nevada", "North Carolina", "Pennsylvania", "Wisconsin"), size = 2000, replace = TRUE)), 
  pollster = factor(sample(levels(harris_data$pollster), size = 2000, replace = TRUE), 
                    levels = levels(harris_data$pollster)), 
  population = factor(sample(levels(harris_data$population), size = 2000, replace = TRUE), 
                    levels = levels(harris_data$population)),
  sample_size = sample(1:2300, size = 2000, replace = TRUE)
)|>
  mutate(
    national_poll = if_else(state == "National", 1, 0),
    recency = as.numeric(difftime(as.Date("2024-11-05"), end_date, units = "days")),
    sample_size_weight = pmin(sample_size / 2300, 1),
    recency_weight = exp(-recency * 0.1),
    combined_weight = recency_weight * sample_size_weight,
    candidate="Kamala Harris"
  )

####### Prediction for Trump ######
new_data_trump <- data.frame(
  end_date = seq(
    min(trump_data$end_date),
    max(trump_data$end_date),
    length.out = 2000
  ),
  pollster = factor(sample(levels(trump_data$pollster), size = 2000, replace = TRUE), 
                    levels = levels(trump_data$pollster)),
 population= factor(sample(levels(trump_data$population), size = 2000, replace = TRUE), 
                    levels = levels(trump_data$population)),
   state = factor(sample( c("National","Arizona", "Georgia", "Michigan", "Nevada", "North Carolina", "Pennsylvania", "Wisconsin"), size = 2000, replace = TRUE), 
                    levels = levels(trump_data$state)),  
  sample_size =sample(1:2300, size = 2000, replace = TRUE),
  pollster_quality= sample(2:4, size = 2000, replace = TRUE)
)|>
  mutate(
   national_poll = if_else(state == "National", 1, 0),
      recency = as.numeric(difftime(as.Date("2024-11-05"), end_date, units = "days")),
    sample_size_weight = pmin(sample_size / 2300, 1),
    recency_weight = exp(-recency * 0.1),  
    combined_weight = recency_weight * sample_size_weight,
    candidate="Donald Trump"
  )
```

@@

## Predicted Voting Outcomes for Recent Three Months by Respondent Group

```{r}
#| echo: false
#| warning: false
#| message: false
#| eval: true
#| fig-cap: "Predicted Support Trends for Kamala Harris and Donald Trump by respondent group using Unweighted Fitted Linear Model"
#| label: fig-support-respondent1
custom_labels <- c("lv" = "Likely Voters", "rv" = "Registered Voters")
### unweighted
ggplot(combined_data_total,aes(x = end_date,y=pct, colour = candidate,size = combined_weight)) +
  geom_point(alpha = 0.1)+ 
  geom_line(data = combined_predictions_filtered,aes(x=end_date,y = predicted_unweighted), size = 1)+ # Smoothed trend line
  facet_wrap(~ population,ncol = 2, labeller = labeller(population = custom_labels)) +
  labs(title = "Predicted Support for Kamala Harris and Donald Trump by respondent group \n in 2024 US Election (From August 1, 2024 to October 27, 2024)",
       subtitle = "predicted using unweighted multiple linear regression model ",
       x = "End Date of the Poll",  # Change x-axis label to End Date
       y = "Predicted Support (%)",
       color = "Candidate",
       size="Weight",
       caption = "Linear Regression Model: Candidate Support Percentage =national_poll + pollster + population") +
  scale_color_manual(values = c("Kamala Harris" = "blue", "Donald Trump" = "red")) +
  theme_classic() +
  theme(legend.position = "top",
        axis.text.x = element_text(angle = 45, hjust = 1),strip.background = element_rect(colour = "black", fill = "white")) +
  scale_x_date(date_labels = "%b %d", date_breaks = "1 week", limits = c(recent_date_cutoff, max_end_date))
```

```{r}
#| echo: false
#| warning: false
#| message: false
#| eval: true
#| fig-cap: "Predicted Support Trends for Kamala Harris and Donald Trump by respondent group using Weighted Fitted Linear Model"
#| label: fig-support-respondent2
### weighted
ggplot(combined_data_total,aes(x = end_date,y=pct, colour = candidate,size = combined_weight)) +
  geom_point(alpha = 0.1)+ 
  geom_line(data = combined_predictions_filtered,aes(x=end_date,y = predicted_weighted), size = 1)+ # Smoothed trend line
  facet_wrap(~ population,ncol = 2, labeller = labeller(population = custom_labels)) +
  labs(title = "Predicted Support for Kamala Harris and Donald Trump by respondent group \n in 2024 US Election (From August 1, 2024 to October 27, 2024)",
       subtitle = "predicted using weighted multiple linear regression model ",
       x = "End Date of the Poll",  # Change x-axis label to End Date
       y = "Predicted Support (%)",
       color = "Candidate",
       size="Weight",
       caption = "Weights: recency_weight * sample_size_weight \nLinear Regression Model: Candidate Support Percentage =national_poll + pollster + population") +
  scale_color_manual(values = c("Kamala Harris" = "blue", "Donald Trump" = "red")) +
  theme_classic() +
  theme(legend.position = "top",
        axis.text.x = element_text(angle = 45, hjust = 1),strip.background = element_rect(colour = "black", fill = "white")) +
  scale_x_date(date_labels = "%b %d", date_breaks = "1 week", limits = c(recent_date_cutoff, max_end_date)) 
```

@@

```{r}
#| echo: false
#| warning: false
#| message: false
#| eval: true
#| fig-cap: "Predicted Support Trends for Kamala Harris and Donald Trump by State using Fitted Linear Model"
#| label: fig-support-state
## unweighted
selected_states <- c("Arizona", "Georgia", "Michigan", "Nevada", "North Carolina", "Pennsylvania", "Wisconsin")
combined_data_total<-combined_data_total|>filter(state %in% selected_states)
combined_predictions_filtered<-combined_predictions_filtered|>filter(state %in% selected_states)
ggplot(combined_data_total,aes(x = end_date,y=pct, colour = candidate)) +
  geom_point(alpha = 0.1)+ 
  geom_line(data = combined_predictions_filtered,aes(x=end_date,y = predicted_unweighted), size = 1)+ # Smoothed trend line
  facet_wrap(~ state,ncol = 4) +
  labs(title = "Predicted Support for Kamala Harris and Donald Trump by State \n in 2024 US Election (From August 1, 2024 to October 27, 2024)",
       subtitle = "predicted using unweighted multiple linear regression model ",
       x = "End Date of the Poll",  # Change x-axis label to End Date
       y = "Predicted Support (%)",
       color = "Candidate",
       caption = "Linear Regression Model: Candidate Support Percentage =national_poll + pollster + population") +
  scale_color_manual(values = c("Kamala Harris" = "blue", "Donald Trump" = "red")) +
  theme_classic() +
  theme(legend.position = "top",
        axis.text.x = element_text(angle = 90, hjust = 1),strip.background = element_rect(colour = "black", fill = "white")) +
  scale_x_date(date_labels = "%b %d", date_breaks = "1 week", limits = c(recent_date_cutoff, max_end_date))
```

@@

## Predicted Support for Harris and Trump by Major Pollsters
```{r}
#| echo: false
#| warning: false
#| message: false
#| eval: true
#| fig-cap: "Predicted Support Trends for Kamala Harris and Donald Trump by Pollster using Unweighted Fitted Linear Model"
#| label: fig-support-pollster1

@@

The predicted support for Kamala Harris and Donald Trump in the upcoming
2024 U.S. presidential election is illustrated in Figure 1. This
analysis spans the period from August 1, 2024, to October 27, 2024, and
uses multiple linear regression models to project voter support.

The unweighted model predictions indicate that Kamala Harris maintains a
consistent support level, with projections hovering around 49%. The blue
dashed line represents this trend, showing only minor fluctuations
throughout the polling period. Conversely, the weighted model for
Harris, indicated by the solid blue line, suggests a slight upward trend
in predicted support, reflecting a potential positive shift in voter
sentiment as the election date approaches.

In contrast, Donald Trump's predicted support is represented by the red
lines. The unweighted model forecasts his support to remain around 48%,
while the weighted model predicts a gradual decline to approximately
46%. The red dashed line indicates the unweighted prediction, whereas
the solid red line shows the weighted prediction. This downward
trajectory may indicate challenges for Trump in sustaining voter
enthusiasm amid changing public opinions.

At the conclusion of the polling period, the models suggest that Kamala
Harris leads Donald Trump by approximately 2.5% in the un-weighted (49%
vs. 46.5%) and 1% in weighted models (49% vs. 48%). Average leading by
about 2%.

@fig-national-support-trendsillustrates illustrates the polling support
trends for Kamala Harris and Donald Trump across the country from August
to October. The scatter points represent individual poll results, with
blue for Harris and red for Trump, while each dot's size reflects the
weight of the poll, accounting for factors like sample size, quality,
and recency. Harris’s support trend line generally remains above
Trump’s, with an average support level around 49%, compared to Trump’s
approximate average of 47% over this period. Toward the end of October,
both candidates show a slight increase, with Harris’s support reaching
just over 50% and Trump’s approaching 49%. This trend suggests a
potential narrowing in support levels as the election approaches,
providing a quantitative snapshot of national polling dynamics.

>>>>

---
title: "Forecasting the 2024 U.S. Presidential Election Using a Model-Based Approach"
subtitle: "Harris expects to win on 49%, leads Trump by about 2% in 2024 US election"
author: 
  - Diana Shen
  - Jinyan Wei
  - Jerry Yu
thanks: "Code and data are available at: [https://github.com/DianaShen1224/Forecast-2024-US-election](https://github.com/DianaShen1224/Forecast-2024-US-election)."
date: today
date-format: long
abstract: "This paper predicts the outcome of the 2024 U.S. presidential election using a statistical model based on aggregated polling data for Kamala Harris and Donald Trump. We employ multi-level regression with post-stratification (MRP) using demographic predictors to estimate voter support. The analysis addresses polling biases and proposes an idealized survey methodology with a $100,000 budget. Our results offer insights into voter behavior and suggest improvements for future election forecasting models."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
editor: 
  markdown: 
    wrap: 72
---

@@

# Introduction {#sec-introduction}

@@

# Data {#sec-data}

## Overview {#sec-data-overview}

@@

## Measurement {#sec-data-measurement}

@@

## Outcome variable {#sec-outcome-variable}

### The support percentage of Kamala Harris.{#sec-harris-support}

@@

## Predictor variables {#sec-predictor-variables}

### End Date {#sec-end-date}

@@

### State {#sec-state}

@@

### Pollster {#sec-pollster}

@@

### Numeric Grade {#sec-numberic-grade}

@@

## Relationships between key varaibles {#sec-data-relationship}

@@

# Model{#sec-model}

@@

## Model Set-Up {#sec-model-setup}

@@

-   **National Poll (`national_poll`)**: Represents the national trend
    in support for the candidate.
-   **Pollster (`pollster`)**: Categorical variable identifying the
    organization conducting the poll, accounting for differences in
    methodology and reliability.
-   **Population (`population`)**: Variable provides an abbreviated description
    of the respondent group, usually indicating their voting status
    (e.g., "lv" for likely voters or "rv" for registered voters).
-   **State (`state`)**: The U.S. state where the poll was conducted or focused,
    if applicable.

### Unweighted Model {#sec-unweighted-model}

@@

$$
y_i | \mu_i, \sigma \sim \text{Normal}(\mu_i, \sigma)
$$ $$
\mu_i = \beta_0 + \beta_1 \cdot \text{National Poll}_i + \beta_2 \cdot \text{Pollster}_i + \beta_3 \cdot \text{Population}_i + \beta_4 \cdot \text{State}_i + \epsilon_i
$$ $$
\epsilon_i \sim \text{Normal}(0, \sigma^2)$$ Where:

-   $\beta_0$ is the intercept term, representing the baseline level of
    support.
-   $\beta_1, \beta_2, \beta_3, \beta_4$ are the coefficients for each predictor,
    indicating their influence on Harris's support percentage.
-   $\sigma^2$ is the variance of the error term, representing
    unobserved variability in support.

@@

### Weighted Model Explanation {#sec-weighted-explain}

@@

- **Combined Weight**: The final weight is the product of all individual weights: $$
\text{Combined Weight} =\text{Recency Weight} \times \text{Sample Size Weight}
$$.

@@

## Model Justification {#sec-model-justify}

@@

# Result {#sec-result}

This section examines the relationship between national polling trends, pollster effects, population demographics, and other factors with respect to the predicted support levels for Kamala Harris and Donald Trump in the 2024 U.S. Presidential Election. Using a dataset comprising polling data from various states and organizations, we applied both unweighted and weighted linear regression models to identify the key predictors influencing each candidate's support. Below, we present the results of our models along with their implications.

Predictions were generated based on our test dataset. However, due to incomplete data for certain states, we were unable to make predictions across the entire U.S. This limitation arises from states with missing values in the dataset, which are consequently not represented in the model, affecting forecast accuracy in those regions.

## Model Results and Interpretation {#sec-result-explain}

The linear regression models constructed for predicting support for Kamala Harris and Donald Trump in the 2024 U.S. Presidential Election utilized both unweighted and weighted configurations. As shown in **Table 1** and **Table 2**, the intercepts for Harris and Trump, estimated at 45.10 and 59.28 respectively in the unweighted models, represent their baseline support levels when all predictors are at reference values. The high \( R^2 \) values of 0.738 for Harris’s unweighted model and 0.860 for her weighted model, along with similar values of 0.635 and 0.890 for Trump, indicate that a significant portion of the variation in support can be explained by the model's predictors. The relatively low Root Mean Square Error (RMSE) values further suggest that the models provide reasonably accurate predictions of support levels.

The results underscore the significance of **national_poll** and **pollster** as key predictors for both candidates' support, highlighting how national trends and pollster differences impact the reported support levels. The **population** predictor further reveals that demographic and regional characteristics contribute meaningfully to support variations, especially in battleground states. These findings enhance our understanding of the dynamics influencing voter sentiment, with methodological and regional factors proving essential in shaping support for each candidate.

@@

## Predicted Voting Outcomes {#sec-model-predicted-outcome}

@fig-support-trend1 and @fig-support-trend2 illustrate the predicted support for Kamala Harris and Donald Trump from August 1, 2024, to October 27, 2024, using both unweighted and weighted linear regression models. In the unweighted model, we see that Trump's predicted support generally hovers between 45% and 50%, while Harris's support ranges from 35% to 45%. Both candidates' support levels appear relatively stable across the polling period, with minor fluctuations. This model, which treats all polls equally, suggests a consistent lead for Trump, albeit within a fairly close range, as shown by the overlapping grey points representing individual poll results.

The weighted model refines these predictions by applying weights based on recency and sample size, which reduces the influence of older or smaller polls. This approach results in smoother trend lines for both candidates, with less apparent variability compared to the unweighted model. Trump's support remains around the mid-40% range, while Harris’s support stays in the high 30% range. The weighting emphasizes more recent and larger polls, likely providing a more accurate reflection of current public opinion. Overall, both models consistently indicate a lead for Trump, with the weighted model slightly stabilizing the predictions.

```{r}
#| echo: false
#| warning: false
#| message: false
#| include: false
#| 
set.seed(233)
####### Prediction for Harris ######
new_data_harris <- data.frame(
  end_date = seq(
    min(harris_data$end_date),
    max(harris_data$end_date),
    length.out = 2000
  ),
  state = factor(sample( c("National","Arizona", "Georgia", "Michigan", "Nevada", "North Carolina", "Pennsylvania", "Wisconsin"), size = 2000, replace = TRUE)), 
  pollster = factor(sample(levels(harris_data$pollster), size = 2000, replace = TRUE), 
                    levels = levels(harris_data$pollster)), 
  population = factor(sample(levels(harris_data$population), size = 2000, replace = TRUE), 
                    levels = levels(harris_data$population)),
  sample_size = sample(1:2300, size = 2000, replace = TRUE)
)|>
  mutate(
    national_poll = if_else(state == "National", 1, 0),
    recency = as.numeric(difftime(as.Date("2024-11-05"), end_date, units = "days")),
    sample_size_weight = pmin(sample_size / 2300, 1),
    recency_weight = exp(-recency * 0.1),
    combined_weight = recency_weight * sample_size_weight,
    candidate="Kamala Harris"
  )

####### Prediction for Trump ######
new_data_trump <- data.frame(
  end_date = seq(
    min(trump_data$end_date),
    max(trump_data$end_date),
    length.out = 2000
  ),
  pollster = factor(sample(levels(trump_data$pollster), size = 2000, replace = TRUE), 
                    levels = levels(trump_data$pollster)),
 population= factor(sample(levels(trump_data$population), size = 2000, replace = TRUE), 
                    levels = levels(trump_data$population)),
   state = factor(sample( c("National","Arizona", "Georgia", "Michigan", "Nevada", "North Carolina", "Pennsylvania", "Wisconsin"), size = 2000, replace = TRUE), 
                    levels = levels(trump_data$state)),  
  sample_size =sample(1:2300, size = 2000, replace = TRUE),
  pollster_quality= sample(2:4, size = 2000, replace = TRUE)
)|>
  mutate(
   national_poll = if_else(state == "National", 1, 0),
      recency = as.numeric(difftime(as.Date("2024-11-05"), end_date, units = "days")),
    sample_size_weight = pmin(sample_size / 2300, 1),
   pollster_quality_weight = pollster_quality / 4,  
    recency_weight = exp(-recency * 0.1),  
    combined_weight = recency_weight * sample_size_weight,
    candidate="Donald Trump"
  )
```

@@

@@

@fig-support-state and @fig-support-state2 compare the predicted support for Kamala Harris and Donald Trump in key battleground states (Arizona, Georgia, Michigan, Nevada, North Carolina, Pennsylvania, and Wisconsin) for the 2024 U.S. election. @fig-support-state uses an unweighted multiple linear regression model, while @fig-support-state2 applies a weighted model, giving greater influence to polls with higher weights based on recency and sample size. In both figures, Trump’s support, represented by red lines, and Harris’s support, shown in blue, show close competition across most states, with slight variations in trends across the polling period from August to October 2024.

The weighted model in @fig-support-state2 introduces subtle shifts, with larger circles indicating polls with greater influence on the predicted trend. This approach captures more recent or higher-quality polls, offering a potentially more accurate representation of voter sentiment shifts over time. The close alignment of support lines for both candidates suggests tight races in these states, which are crucial for the election outcome. The use of weighted and unweighted models highlights the importance of data weighting in enhancing the reliability of electoral forecasts in dynamic political environments.
```{r}
#| echo: false
#| warning: false
#| message: false
#| eval: true
#| fig-cap: "Predicted Support Trends for Kamala Harris and Donald Trump by State using Fitted Linear Model"
#| label: fig-support-state
## unweighted
selected_states <- c("Arizona", "Georgia", "Michigan", "Nevada", "North Carolina", "Pennsylvania", "Wisconsin")
combined_data_total<-combined_data_total|>filter(state %in% selected_states)
combined_predictions_filtered<-combined_predictions_filtered|>filter(state %in% selected_states)
ggplot(combined_data_total,aes(x = end_date,y=pct, colour = candidate)) +
  geom_point(alpha = 0.1)+ 
  geom_line(data = combined_predictions_filtered,aes(x=end_date,y = predicted_unweighted), size = 1)+ # Smoothed trend line
  facet_wrap(~ state,ncol = 4) +
  labs(title = "Predicted Support for Kamala Harris and Donald Trump by State \n in 2024 US Election (From August 1, 2024 to October 27, 2024)",
       subtitle = "predicted using unweighted multiple linear regression model ",
       x = "End Date of the Poll",  # Change x-axis label to End Date
       y = "Predicted Support (%)",
       color = "Candidate",
       caption = "Linear Regression Model: Candidate Support Percentage =national_poll + pollster + population") +
  scale_color_manual(values = c("Kamala Harris" = "blue", "Donald Trump" = "red")) +
  theme_classic() +
  theme(legend.position = "top",
        axis.text.x = element_text(angle = 90, hjust = 1),strip.background = element_rect(colour = "black", fill = "white")) +
  scale_x_date(date_labels = "%b %d", date_breaks = "1 week", limits = c(recent_date_cutoff, max_end_date))
```

@@

## Predicted Support for Harris and Trump by Major Pollsters

@fig-support-pollster1 and @fig-support-pollster2 depict the predicted support for Kamala Harris and Donald Trump in the 2024 U.S. election, from August 1, 2024, to October 27, 2024, using a weighted multiple linear regression model. The red line shows fluctuations in Trump’s support, generally between 40% and 55%, with some noticeable peaks and dips, indicating variability over time. In contrast, Harris’s support, represented by the blue line, remains more stable, consistently ranging around 40% to 50%, suggesting less volatility in voter sentiment for her.

Pollsters such as AtlasIntel, Emerson, Beacon/Shaw, Siena/NY, and YouGov are represented by different colors, with circle sizes reflecting weights based on factors like recency and sample size. Larger circles correspond to higher-weighted polls, indicating they had a greater influence on the predictions. The model incorporates national poll data, adjustments for pollster effects, and population considerations, allowing for a refined prediction approach. This approach ensures that more recent and larger polls play a more significant role, capturing shifts in voter sentiment as the election approaches.
```{r}
#| echo: false
#| warning: false
#| message: false
#| eval: true
#| fig-cap: "Predicted Support Trends for Kamala Harris and Donald Trump by Pollster using Unweighted Fitted Linear Model"
#| label: fig-support-pollster1

@@
